Biden More Favorable Among Female, Black, Asian, Hispanic, Middle Eastern, and Non-gun Owning Voters in the 2020 US Presidential Election

### 2024-03-17 paper/paper.qmd
Updata subsections of the data section of paper

## Sources and Methodology

@@

@@

## Variables and Measurement

@@

In this paper, we measured key variables related to voter behaviour. From the dataset, we selected `gender`, `race`, `gunown`. In Figure 1, we can see support for candidate based on gender and race. For gender, we considered two options, male or female. For race, we considered eight options, White, Black, Hispanic, Asian, Native American, Middle Eastern, two or more races, and other. Note that only one selection was allowed in the original study for both gender and race. Figure 2 illustrates the support for each candidate based on gun ownership status, with four options. Individuals who personally own a gun, who don’t personally own one, but someone in their household owns a gun, no one in the household owns a gun, and not sure. We also selected the variable that recorded whether an individual voted for Biden or Trump in the 2020 Presidential election, `CC20_410`. This allowed us to establish a binary outcome variable for the probability of voting Biden or Trump in our model in @sec-model. The variables measured here allowed us to identify variation in political attitudes and voting patterns.

@@

>>>>

## Sources

@@

## Methodology

@@

## Variables

@@

From the dataset, we selected `gender`, `race`, `gunown` from the pre-election questionnaire. In @fig-race-gender, we can see support for candidate based on gender and race. For gender, we were given two options in the study, male or female. For race, we considered eight options, White, Black, Hispanic, Asian, Native American, Middle Eastern, two or more races, and other. Note that only one selection was allowed in the original study for both gender and race. @fig-gun-ownership-gender illustrates the support for each candidate based on gun ownership status, with four options. Individuals who personally own a gun, who don’t personally own one, but someone in their household owns a gun, no one in the household owns a gun, and not sure. We also selected a variable from the post-election questionnaire, the variable that recorded whether an individual voted for Biden or Trump in the 2020 Presidential election, `CC20_410`. This allowed us to establish a binary outcome variable for the probability of voting Biden or Trump in our model in @sec-model.

@@

## Measurement
